# Pre-workshop tasks {#sec-pre-workshop}

```{r}
#| echo: false
# To trigger downlit.
```

In order to participate in this workshop, you must complete everything in
this pre-workshop tasks section and finish with **completing the
[survey]()** at the end. These tasks are designed to make it easier for
everyone to start the workshop with everything set up. For some of the
tasks, you might not understand why you need to do them, but you will
likely understand why once the workshop begins.

Depending on your skills and knowledge, these tasks could take between
**3-5 hrs to finish**, so we suggest planning a full day to complete
them. Depending on your institution and how they handle installing
software on work computers, you also might have to contact IT *very
early* to make sure everything is properly installed and setup.

## Summary of tasks

Here's a quick overview of the tasks you need to do. Specific details
about them are found as you work through the tasks.

1.  Install a version of R, RStudio, Quarto, and Git that is as updated
    as possible. For some people, depending on their institution, this
    task can take the **longest amount of time** because you have to
    contact your IT to install these packages.
2.  Install necessary R packages.
3.  TODO: Add more tasks
4.  Read the syllabus (@sec-syllabus).
5.  Read the [Code of
    Conduct](https://guides.rostools.org/conduct.html).
6.  Complete the pre-workshop [survey](): This survey is pretty quick,
    maybe \~10 minutes. There will be some bits from the tasks that you
    will need to paste into this survey.

Check each section for exact details on completing these tasks.

## Learning objective

In general, these pre-workshop tasks are meant to help prepare you for the
workshop and make sure everything is setup properly so the first session
runs smoothly. However, some of these tasks are meant for learning as
well as for general setup, so we have defined the following learning
objectives for this page:

1.  TODO: List objectives

## Reading the workshop website {#sec-reading-website}

```{r}
#| echo: false
#| eval: true
#| results: asis
cat(r3admin::read_common("reading-website.md"), sep = "\n")
```

## Installing the latest programs {#sec-install-programs}

```{r}
#| echo: false
#| eval: true
#| results: asis
cat(r3admin::read_common("installing-programs.md"), sep = "\n")
```

## TODO: Next section

## Workshop basics

If you haven't read the syllabus, **please read it now**. Read over what
the workshop will cover, what we expect you to learn by the end of it, and
what our basic assumptions are about who you are and what you already
know. At the end of this section, we'll ask you a few questions to see
if you understand what you'll learn in the workshop.

One goal of the workshop is to teach about open science, and true to our
mission, we practice what we preach. The workshop material is publicly
accessible (all on this website) and [openly licensed]() so you can
(re-)use it for free! The material is organized in the order that we
will cover it in the workshop.

We have a [Code of Conduct](https://guides.rostools.org/conduct.html).
If you haven't read it, **read it now**. The survey involves a question
about Conduct. We want to make sure this workshop is a supportive and safe
environment for learning, so this Code of Conduct is quite important.

You're almost done. Please fill out the pre-workshop survey to finish this
section, either [at this link]().

See you at the workshop!
